---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Validation for Two-Way Mixed (between by within) ANOVA

I've previously developed a code for a power simulation of a 2 (between) and 5 (within) ANOVA. We can test this code against Daniel Lakens ANOVA simluation code to see if the two are in agreement


## Installation

We install the functions:

```{r}
# Install the two functions from Lakens GitHub by running the code below:

source("https://raw.githubusercontent.com/Lakens/ANOVA_power_simulation/master/ANOVA_design.R")
source("https://raw.githubusercontent.com/Lakens/ANOVA_power_simulation/master/ANOVA_power.R")

#Install the function from Caldwell GitHub by running the code below:

source("https://raw.githubusercontent.com/arcaldwell49/PowerSims-AC/master/2b5ANOVAsim.R")
```

## Type 1 error (i.e., no effect)

We can simulate a null effect by setting all the means to zero. I had an initial concern that the Lakens code would have the between subjects factors would be correlated. We can test this against my code by varying the correlation. The "power" for all effects should by 5% for all effects.  This simulation should yield a very small effect size (0.025).


```{r, message=FALSE, warning=FALSE}
#Test type 1 error rate
#With correlation of 0.5
Cald_Nulln20r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, TEt1Mean=0, TEt2Mean=0,TEt3Mean=0, TEt4Mean=0, TEt5Mean=0,
             r=0.5, SD=1, sample=20, reps=10000,  sig = 0.05)

design_Nulln20_r5 <- ANOVA_design(string = "2b*5w",
                              n = 20, 
                              mu = c(0, 0, 0, 0, 0,
                                     0, 0, 0, 0, 0), 
                              sd = 1, 
                              r=0.5, 
                              p_adjust = "none")

Lakens_Nulln20_r5 <- ANOVA_power(design_Nulln20_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Nulln20_r5$main_results))

knitr::kable(as.data.frame(Cald_Nulln20r5$Simulation_Result))

#With correlation of 0.65
Cald_Nulln20r65 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, TEt1Mean=0, TEt2Mean=0,TEt3Mean=0, TEt4Mean=0, TEt5Mean=0,
                               r=0.65, SD=1, sample=20, reps=10000,  sig = 0.05)

design_Nulln20_r65 <- ANOVA_design(string = "2b*5w",
                                  n = 20, 
                                  mu = c(0, 0, 0, 0, 0,
                                         0, 0, 0, 0, 0), 
                                  sd = 1, 
                                  r=0.65, 
                                  p_adjust = "none")

Lakens_Nulln20_r65 <- ANOVA_power(design_Nulln20_r65, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Nulln20_r65$main_results))

knitr::kable(as.data.frame(Cald_Nulln20r65$Simulation_Result))

#With correlation of 0.8
Cald_Nulln20r8 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, TEt1Mean=0, TEt2Mean=0,TEt3Mean=0, TEt4Mean=0, TEt5Mean=0,
                                r=0.8, SD=1, sample=20, reps=10000,  sig = 0.05)

design_Nulln20_r8 <- ANOVA_design(string = "2b*5w",
                                   n = 20, 
                                   mu = c(0, 0, 0, 0, 0,
                                          0, 0, 0, 0, 0), 
                                   sd = 1, 
                                   r=0.8, 
                                   p_adjust = "none")

Lakens_Nulln20_r8 <- ANOVA_power(design_Nulln20_r8, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Nulln20_r8$main_results))

knitr::kable(as.data.frame(Cald_Nulln20r8$Simulation_Result))

```



## Interaction effect

This simulation is for an interaction effect wherein are expecting no change in the control group and a 0.2 SD increase in the mean at every time point. In the simulations we will vary the correlation between measures and the sample size.




```{r, message=FALSE, warning=FALSE}
#Power for interaction
#With correlation of 0.5 and sample size of 20
Cald_Inter_n20_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                  TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                               r=0.5, SD=1, sample=20, reps=10000,  sig = 0.05)

design_Inter_n20_r5 <- ANOVA_design(string = "2b*5w",
                                  n = 20, 
                                  mu = c(0, 0, 0, 0, 0,
                                         0, 0.2, 0.4, 0.6, 0.8), 
                                  sd = 1, 
                                  r=0.5, 
                                  p_adjust = "none")

Lakens_Inter_n20_r5 <- ANOVA_power(design_Inter_n20_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Inter_n20_r5$main_results))

knitr::kable(as.data.frame(Cald_Inter_n20_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 20
Cald_Inter_n20_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                  TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                  r=0.75, SD=1, sample=20, reps=10000,  sig = 0.05)

design_Inter_n20_r75 <- ANOVA_design(string = "2b*5w",
                                    n = 20, 
                                    mu = c(0, 0, 0, 0, 0,
                                           0, 0.2, 0.4, 0.6, 0.8), 
                                    sd = 1, 
                                    r=0.75, 
                                    p_adjust = "none")

Lakens_Inter_n20_r75 <- ANOVA_power(design_Inter_n20_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Inter_n20_r75$main_results))

knitr::kable(as.data.frame(Cald_Inter_n20_r75$Simulation_Result))


#With correlation of 0.5 and sample size of 40
Cald_Inter_n40_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                  TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                  r=0.5, SD=1, sample=40, reps=10000,  sig = 0.05)

design_Inter_n40_r5 <- ANOVA_design(string = "2b*5w",
                                    n = 40, 
                                    mu = c(0, 0, 0, 0, 0,
                                           0, 0.2, 0.4, 0.6, 0.8), 
                                    sd = 1, 
                                    r=0.5, 
                                    p_adjust = "none")

Lakens_Inter_n40_r5 <- ANOVA_power(design_Inter_n40_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Inter_n40_r5$main_results))

knitr::kable(as.data.frame(Cald_Inter_n40_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 40
Cald_Inter_n40_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                   TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                   r=0.75, SD=1, sample=40, reps=10000,  sig = 0.05)

design_Inter_n40_r75 <- ANOVA_design(string = "2b*5w",
                                     n = 40, 
                                     mu = c(0, 0, 0, 0, 0,
                                            0, 0.2, 0.4, 0.6, 0.8), 
                                     sd = 1, 
                                     r=0.75, 
                                     p_adjust = "none")

Lakens_Inter_n40_r75 <- ANOVA_power(design_Inter_n40_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_Inter_n40_r75$main_results))

knitr::kable(as.data.frame(Cald_Inter_n40_r75$Simulation_Result))



```



## Main Effect: Between Subjects 

This simulation is for a main effect between subjects wherein we are expecting the experimental group is 0.5 SD higher than the control at all time point. In the simulations we will vary the correlation between measures and the sample size. 


```{r, message=FALSE, warning=FALSE}
#Power for Main Effect for between subjects
#With correlation of 0.5 and sample size of 20
Cald_MainB_n20_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                  TEt1Mean=0.5, TEt2Mean=0.5,TEt3Mean=0.5, TEt4Mean=0.5, TEt5Mean=0.5,
                                  r=0.5, SD=1, sample=20, reps=10000,  sig = 0.05)

design_MainB_n20_r5 <- ANOVA_design(string = "2b*5w",
                                    n = 20, 
                                    mu = c(0, 0, 0, 0, 0,
                                           0.5, 0.5, 0.5, 0.5, 0.5), 
                                    sd = 1, 
                                    r=0.5, 
                                    p_adjust = "none")

Lakens_MainB_n20_r5 <- ANOVA_power(design_MainB_n20_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainB_n20_r5$main_results))

knitr::kable(as.data.frame(Cald_MainB_n20_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 20
Cald_MainB_n20_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                   TEt1Mean=0.5, TEt2Mean=0.5,TEt3Mean=0.5, TEt4Mean=0.5, TEt5Mean=0.5,
                                   r=0.75, SD=1, sample=20, reps=10000,  sig = 0.05)

design_MainB_n20_r75 <- ANOVA_design(string = "2b*5w",
                                     n = 20, 
                                     mu = c(0, 0, 0, 0, 0,
                                            0.5, 0.5, 0.5, 0.5, 0.5), 
                                     sd = 1, 
                                     r=0.75, 
                                     p_adjust = "none")

Lakens_MainB_n20_r75 <- ANOVA_power(design_MainB_n20_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainB_n20_r75$main_results))

knitr::kable(as.data.frame(Cald_MainB_n20_r75$Simulation_Result))

#With correlation of 0.5 and sample size of 40
Cald_MainB_n40_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                  TEt1Mean=0.5, TEt2Mean=0.5,TEt3Mean=0.5, TEt4Mean=0.5, TEt5Mean=0.5,
                                  r=0.5, SD=1, sample=40, reps=10000,  sig = 0.05)

design_MainB_n40_r5 <- ANOVA_design(string = "2b*5w",
                                    n = 40, 
                                    mu = c(0, 0, 0, 0, 0,
                                           0.5, 0.5, 0.5, 0.5, 0.5), 
                                    sd = 1, 
                                    r=0.5, 
                                    p_adjust = "none")

Lakens_MainB_n40_r5 <- ANOVA_power(design_MainB_n40_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainB_n40_r5$main_results))

knitr::kable(as.data.frame(Cald_MainB_n40_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 40
Cald_MainB_n40_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0, TCt3Mean=0, TCt4Mean=0, TCt5Mean=0, 
                                   TEt1Mean=0.5, TEt2Mean=0.5,TEt3Mean=0.5, TEt4Mean=0.5, TEt5Mean=0.5,
                                   r=0.75, SD=1, sample=40, reps=10000,  sig = 0.05)

design_MainB_n40_r75 <- ANOVA_design(string = "2b*5w",
                                     n = 40, 
                                     mu = c(0, 0, 0, 0, 0,
                                            0.5, 0.5, 0.5, 0.5, 0.5), 
                                     sd = 1, 
                                     r=0.75, 
                                     p_adjust = "none")

Lakens_MainB_n40_r75 <- ANOVA_power(design_MainB_n40_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainB_n40_r75$main_results))

knitr::kable(as.data.frame(Cald_MainB_n40_r75$Simulation_Result))

```


## Main Effect: Within Subjects 

This simulation is for a main effect within subjects (repeated measures) wherein we are expecting the experimental group is 0.5 SD higher than the control at all time point. In the simulations we will vary the correlation between measures and the sample size. 

```{r, message=FALSE, warning=FALSE}
#Power for iMain Effect for within subjects factor
#With correlation of 0.5 and sample size of 20
Cald_MainW_n20_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0.2,TCt3Mean=0.4, TCt4Mean=0.6, TCt5Mean=0.8, 
                                  TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                  r=0.5, SD=1, sample=20, reps=10000,  sig = 0.05)

design_MainW_n20_r5 <- ANOVA_design(string = "2b*5w",
                                    n = 20, 
                                    mu = c(0, 0.2, 0.4, 0.6, 0.8,
                                           0, 0.2, 0.4, 0.6, 0.8), 
                                    sd = 1, 
                                    r=0.5, 
                                    p_adjust = "none")

Lakens_MainW_n20_r5 <- ANOVA_power(design_MainW_n20_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainW_n20_r5$main_results))

knitr::kable(as.data.frame(Cald_MainW_n20_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 20
Cald_MainW_n20_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0.2,TCt3Mean=0.4, TCt4Mean=0.6, TCt5Mean=0.8,
                                   TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                   r=0.75, SD=1, sample=20, reps=10000,  sig = 0.05)

design_MainW_n20_r75 <- ANOVA_design(string = "2b*5w",
                                     n = 20, 
                                     mu = c(0, 0.2, 0.4, 0.6, 0.8,
                                            0, 0.2, 0.4, 0.6, 0.8), 
                                     sd = 1, 
                                     r=0.75, 
                                     p_adjust = "none")

Lakens_MainW_n20_r75 <- ANOVA_power(design_MainW_n20_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainW_n20_r75$main_results))

knitr::kable(as.data.frame(Cald_MainW_n20_r75$Simulation_Result))

#With correlation of 0.5 and sample size of 40
Cald_MainW_n40_r5 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0.2,TCt3Mean=0.4, TCt4Mean=0.6, TCt5Mean=0.8, 
                                  TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                  r=0.5, SD=1, sample=40, reps=10000,  sig = 0.05)

design_MainW_n40_r5 <- ANOVA_design(string = "2b*5w",
                                    n = 40, 
                                    mu = c(0, 0.2, 0.4, 0.6, 0.8,
                                           0, 0.2, 0.4, 0.6, 0.8), 
                                    sd = 1, 
                                    r=0.5, 
                                    p_adjust = "none")

Lakens_MainW_n40_r5 <- ANOVA_power(design_MainW_n40_r5, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainW_n40_r5$main_results))

knitr::kable(as.data.frame(Cald_MainW_n40_r5$Simulation_Result))

#With correlation of 0.75 and sample size of 40
Cald_MainW_n40_r75 <- ANOVAsim2by5(TCt1Mean=0, TCt2Mean=0.2,TCt3Mean=0.4, TCt4Mean=0.6, TCt5Mean=0.8, 
                                   TEt1Mean=0, TEt2Mean=0.2,TEt3Mean=0.4, TEt4Mean=0.6, TEt5Mean=0.8,
                                   r=0.75, SD=1, sample=40, reps=10000,  sig = 0.05)

design_MainW_n40_r75 <- ANOVA_design(string = "2b*5w",
                                     n = 40, 
                                     mu = c(0, 0.2, 0.4, 0.6, 0.8,
                                            0, 0.2, 0.4, 0.6, 0.8), 
                                     sd = 1, 
                                     r=0.75, 
                                     p_adjust = "none")

Lakens_MainW_n40_r75 <- ANOVA_power(design_MainW_n40_r75, alpha = 0.05, nsims = 10000)

#Compare the two results
knitr::kable(as.data.frame(Lakens_MainW_n40_r75$main_results))

knitr::kable(as.data.frame(Cald_MainW_n40_r75$Simulation_Result))

```

```{r echo=FALSE}
save.image("C:/Users/ac039/Dropbox/Statistics/PowerSims-AC/objects_for_markdown.RData")
```

